---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  color: #194761;
  background-color: #D9D9D9;
  font-family: 'Segoe UI'
}
```

## This dynamic report tracks my performance from daily races in the game Le Mans Ultimate.

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTXHwT73wmXutjHiMkIcBhKrB4vywWw4nQaIL73jXNJRQncIWTACNo7iLGn7XwfJ2hHBwJpgwA0AzNH/pub?gid=268033178&single=true&output=csv")

latest_data <- logged_data %>%
  rename(track = 2,
         quali_position = 3,
         race_position = 4,
         split_number = 5,
         total_splits = 6)

plot_title <- "Le Mans Ultimate Statistics"
plot_caption <- "Source: Le Mans Ultimate Driver Profile"

# Qualifying position at each track
quali_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = latest_data$quali_position, fill = track)) + 
  labs(title = plot_title,
       subtitle = "Qualifying Position",
       caption = plot_caption,
       x = "Qualifying Position",
       y = "Count")

mean_qualifying <- latest_data$quali_position %>%
  mean() %>%
  round(1)

median_qualifying <- latest_data$quali_position %>%
  median()

# Race finishing position at each track
race_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = latest_data$race_position, fill = track)) + 
  labs(title = plot_title,
       subtitle = "Race Finishing Position",
       caption = plot_caption,
       x = "Race Position",
       y = "Count")

mean_race <- latest_data$race_position %>%
  mean() %>%
  round(1)

median_race <- latest_data$race_position %>%
  median()

# Positions gained plot
positions_gained_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = quali_position - race_position, fill = track)) + 
  labs(title = plot_title,
       subtitle = "Positions Gained in the Race",
       caption = plot_caption,
       x = "Positions Gained",
       y = "Count")

median_positions_gained <- (latest_data$quali_position - latest_data$race_position) %>%
  median()

# Total Races plot
total_races_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = track),
           fill = "#3691cf") + 
  labs(title = plot_title,
       subtitle = "Total races at each track",
       caption = plot_caption,
       x = "Track",
       y = "Total Races")

total_races_count <- latest_data$track %>%
  length()
```

```{r fig.width = 10, fig.height = 6}
quali_plot
```

#### The mean qualifying position was `r mean_qualifying` and the median qualifying position was `r median_qualifying`

```{r fig.width = 10, fig.height = 6}
race_plot
```

#### The mean race position was `r mean_race` and the median race position was `r median_race`

```{r fig.width = 10, fig.height = 6}
positions_gained_plot
```

#### The median positions gained was `r median_positions_gained`

```{r fig.width = 10, fig.height = 6}
total_races_plot
```

#### Total races: `r total_races_count`